Left-linear rules in adhesive categories

### 2024-02-14 icalp/fusione.tex
minima e esempio egraphs

\begin{definition}[Graph signature]
  Let $\mathcal{G}=(V, E, s, t)$, with $s,t\colon E\rightrightarrows V$, be a finite directed acyclic graph,
  we define the \emph{depth} of a vertex $v\in V$ as
  \[
    \dph(v)=\begin{cases}
      0 & \text{there is no $e\in E$ such that $t(e)=v$}\\
      m+1 &\text{where } m=\min\{\dph(s(e)) \mid e\in E \text{ such that } t(e)=v
      \} 
    \end{cases}
  \]
\end{definition}

@@

  Explicitly, an
  e-graph $G = \langle s_G, t_G, q_G \rangle$ where
  $s_G, t_G: E_G \rightrightarrows V_G$ provides the graphical
  structure, while the surjective function $q_G : V_G \to Q_G$ maps
  each node to the corresponding equivalence class. Notice that the inclusion functor into  $[E \rightrightarrows V \to Q, \cat{Set}]$ creates pullbacks and pushouts \cite{mac2013categories} so that they are computed componentwise.

@@

As in \cite{BaldanGM06}, one can study  left-linear rewriting systems  on $\cat{eGraphs}$ in which the right half of a rule is mono but not regular in general, allowing us to identify, but not merging, more nodes . These rewring systems are well-switching.
\end{example}

>>>>

\begin{definition}[Graph signature]
  Let $\mathcal{G}=(V, E, s, t)$ be a finite directed acyclic graph where $s,t\colon E\rightrightarrows V$.
  We define the \emph{depth} of a vertex $v\in V$ as
  \[
    \dph(v)=\begin{cases}
      0 & \text{there is no $e\in E$ such that $t(e)=v$}\\
      m+1 &\text{where } m=\min\{\dph(s(e)) \mid e\in E \text{ such that } t(e)=v
      \} 
    \end{cases}
  \]
\end{definition}

@@

  Explicitly, an
  e-graph $G$ is a triple $\langle s_G, t_G, q_G \rangle$ where
  $s_G, t_G: E_G \rightrightarrows V_G$ provides the graphical
  structure, while the surjective function $q_G : V_G \to Q_G$ maps
  each node to the corresponding equivalence class. Notice that the inclusion functor into  $[E \rightrightarrows V \to Q, \cat{Set}]$ creates pullbacks and pushouts \cite{mac2013categories} so that they are computed componentwise.

@@

Left-linear rewriting systems on $\cat{eGraphs}$, i.e. in which the right half of a rule is mono but not regular in general, 
are well-switching. They have been used in~\cite{BaldanGM06} for the graphical implementation of nominal calculi, where,
differently from~\cite{Gad07}, as a result of name passing the received name is not merged with a local one at the receiver,
but put instead in the same equivalence class, thus better tracing the causal dependencies among processes reductions.
\end{example}
